BOLD Parameter Estimation Using Particle Filters

### 2010-08-11 doc/thesis/conclusion.tex
conclusion-ed

Many of the approaches to determining areas of neural activation aim
to be Bayesian, yet ultimately must make limiting assumptions about
the distributions that turn the approach into classical statistics. 
This approach is a true Bayesian non-parametric approach that given
enough measurements will approach the true probability distribution
of the parameters. While the conclusion that the parameters are not
uniquely identifiable is a disappointing in light years of research 
attempting to learn these parameters, it in fact further demonstrates
the need to estimate probability distribution rather than a single 
parameter estimate.

>>>>

Many of the approaches to determining areas of neural activation aim
to be Bayesian, yet ultimately must make limiting assumptions about
the distributions that turn the approach into classical statistics. 
This approach is a true Bayesian non-parametric approach that given
enough measurements will approach the true probability distribution
of the parameters. While the conclusion that the parameters are not
uniquely identifiable is a disappointing one in light years of research 
attempting to learn these parameters, it in fact further demonstrates
the need to estimate probability distribution rather than a single 
parameter estimate. At the same time, the output of the particle filter
is still about to give good estimates of the BOLD output, and not
dependent on heavy Gaussian smoothing. Therefore, all the current 
experimental paradigms to determine regional activity are still viable.
To borrow a computer term, the particle filter algorithm is backward 
compatible with the current methods.

Concluding, the particle filter provides comparable performance with
conventional tests, but also provides a platform for a wide range of
future uses beyond what is possible with the methods applied in the
past.
